\FloatBarrier \begin{oframed}\textbf{Valid Stock \& Variable Connections} 

 The following sequence presents, and explains, the valid connections for elements of a simulation model.

\begin{enumerate}
\item Create a new \a{Stock} named \p{Stock 1}.
\item 

A \p{Stock} represents a quantity of something that will increase or decrease during the simulation.


\item Create a new \a{Flow} going from empty space to the primitive \p{Stock 1}. Name that flow \p{Flow 1}.
\item 

A \p{Stock} can only change via a \p{Flow}. To create an inflow first create an outflow and then select \p{Reverse} to change the direction of the flow. This is just a quirk of the environment. A flow that doesn't have a specific origin simply means we're not concerned with where the flow comes from. When you fill the bathtub do you think about where the water comes from?


\item Create a new \a{Stock} named \p{Stock 2}.
\item Create a new \a{Flow} going from the primitive \p{Stock 1} to the primitive \p{Stock 2}. Name that flow \p{Flow 2}.
\item 

A \p{Flow} can move stuff from one \p{Stock} to another. \p{Stock 1} decreases by the same amount that \p{Stock 2} increases. Flows need to be conserved because you can't create something form nothing in a model.


\item Create a new \a{Flow} going from the primitive \p{Stock 2} to empty space. Name that flow \p{Flow 3}.
\item 

A \p{Flow} that doesn't have a specific destination simply means we're not concerned with where the \p{Flow} goes.



\end{enumerate} \end{oframed}

